manuscript

### 2023-11-29 scripts/manuscript.qmd
Danielle's Peer Review

---
title: "manuscript"
format: pdf
editor: visual
author: "Leah Peterson, Alexus Rock, and Ben Pfingston"
---

@@

```{r}
#| label: scatterplot
#| warning: false
#| message: false
#| echo: false

>>>>

---
title: "manuscript"
format: pdf
editor: visual
author: "Leah Peterson, Alexus Rock, and Ben Pfingston"
---
```{r}
# Hi! Danielle here. Your code looks so clean! It is super easy to follow.
# All of your data and figures loaded properly too. Great job!
# I have never seen the "scale_x_discrete" code before so I definitely learned that from your code.
# I really appreciated how you left a note in your code explaining the new labels/why you labeled something the way you did for your collaborators. Super helpful!
# I noticed that you labeled all the code chunks with box plots so I made a label from your code chunk for the scatter plot following the same format - "scatterplot-ss-score-ppis-total"
```

@@

```{r scatterplot-ss-score-ppis-total}
#| label: scatterplot
#| warning: false
#| message: false
#| echo: false
